Supporting Information

### 2017-01-06 portfolio/text/anderson-etal-rev-pfx.tex
Move dual fig 4 to supp
Fix bib; add outline
Edits
Jordan and Milo edits

\title{
  Benefits and risks of diversification\\ for individual fishers\\
  Benefits of diversification and risks of 
  changing strategies for individual fishers\\
Benefits of diversification are unavailable to many fishermen\\
}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Andrew O. Shelton$^2$,\\
Jennifer C. Shriver,
Jordan T. Watson$^X$,
\ldots
}

\newlabel{tab:strategies}{1}
\newlabel{fig:fe}{1}
\newlabel{fig:re}{2}
\newlabel{fig:spoke-all}{3}
\newlabel{fig:resid}{4}
\newlabel{fig:resid-downside}{5}
\newlabel{fig:str-yrs}{6}
\newlabel{fig:ifq}{7}

@@

@@

@@

\noindent
$^X$Ted Stevens Marine Research Institute, Alaska Fisheries Science Center, 17109
Pt Lena Loop Road, Juneau, AK 99801, USA

\noindent
Affiliations \ldots

@@

% \vspace{-1cm}

%\input{../analysis/values} % R output

>>>>

\title{
  Benefits and risks of diversification\\ for individual fishers
  % Benefits of diversification and risks of 
  % changing strategies for individual fishers\\
% Benefits of diversification are unavailable to many fishermen\\
}
\author{
Sean C. Anderson$^1$,
Eric J. Ward$^2$,
Andrew O. Shelton$^2$,\\
Milo D. Adkison$^3$,
Anne H. Beaudreau$^3$,\\
Richard E. Brenner$^4$,
Alan C. Haynie$^5$,
Jennifer C. Shriver$^4$,
Jordan T. Watson$^6$,
\ldots
}

\newlabel{tab:strategies}{1}
\newlabel{fig:fe}{1}
\newlabel{fig:re}{2}
\newlabel{fig:spoke-all}{3}
\newlabel{fig:resid}{4}
\newlabel{fig:resid-downside}{5}
\newlabel{fig:str-yrs}{6}
\newlabel{fig:ifq}{7}
\newlabel{fig:mirror}{8}
\newlabel{fig:noeffort}{9}

@@

% TODO: standardize and complete addresses

@@

\noindent
$^3$College of Fisheries and Ocean Sciences, University of Alaska Fairbanks,
17101 Point Lena Loop Rd, Juneau, AK, 99801, USA

\noindent
$^4$Alaska Department of Fish and Game, Commercial Fisheries Division, Cordova, USA

@@

\noindent
$^6$NOAA / National Marine Fisheries Service, Alaska Fisheries Science Center, Auke
Bay Laboratories, 17109 Pt. Lena Loop Rd., Juneau, AK 99801, USA

@@

### 2017-01-06 portfolio/text/ms.Rmd
Jordan and Milo edits

Individuals relying on the extraction of natural resources for their livelihood
--- fishers, farmers, miners, and loggers, among others --- face high levels of
income variability driven by a mix of environmental, biological, management, and
economic variability. A key component to managing these industries is
identifying how regulatory actions and individual behaviour affect income
variability and by extension the economic stability and sustainable use of
natural resources. For commercial fisheries, recent work has identified that
communities and vessels fishing a greater diversity of species have less revenue
variability than those fishing a lower diversity. However, it is unclear if
these benefits extend to the actions of individual fishers and how year-to-year
changes in diversification affect revenue and revenue variability. Here, we
identify three axes by which fishers in Alaska, one of the world's most
productive fishing regions, can diversify fishing activities. We show that,
despite increasing specialization over the last 30 years, fishing permits with
higher species diversity reduces individual revenue variability and fishing an
additional permit is associated with higher revenue and lower variability.
However, increasing species diversity within the constraints of existing permits
has a fishery-dependent effect on revenue and is usually (`r g2_dens`%
probability) associated with increased revenue uncertainty the following year.
Our results demonstrate that the most effective option for individuals to
decrease revenue variability is to purchase permits to participate in additional
or more diverse fisheries. However, this option is expensive, often limited by
regulations such as catch share programs, and consequently unavailable to many
individuals. With increasing environmental variability in a changing climate, it
will be particularly important that individuals relying on natural resources for
their livelihood have effective strategies to reduce income variability.

@@

Individuals who rely on natural resources for income develop strategies to
reduce income variability. For example, farmers may rotate their crops to buffer
short-term climate variation and long-term environmental trends [@zentner1988].
Similarly, loggers maintain a diverse mix of tree species, age structure, and
harvest in geographical areas to buffer against disease outbreak, wildfires, and
price variation (REF). However, external forces may restrict the available
options to dampen income variability. Otherwise well-intentioned regulations may
limit how individuals diversify, or incentivize against diversification. For
example, in terrestrial agriculture, crop subsidies in the U.S. may incentivize
some farms to specialize (e.g. dairy, grains, soybeans; @mishra2002). In other
instances, external market forces (e.g. prices or demand) may discourage the
adoption of diverse strategies and help promote specialization [@bradshaw2004].

@@

The state and federal fisheries of Alaska provide a unique opportunity to
understand the role of individuals' strategies in determining income and income
variability. Fisheries in Alaska are among the highest-valued fisheries in the
world with ~2.7 billion kg landed biomass valued at nearly 2 billion USD
annually [@nmfs2016]. The days of open, unregulated fisheries in most developed
countries have passed --- fishers must own a license to participate in virtually
all fisheries [@hilborn2003a]. While such regulations have helped reduce
overfishing, they limit the available strategies to reduce income variability.
For example, many permits limit fishing to a single species, diversifying by
purchasing additional fishing permits can be expensive[^1], and some fisheries
limit the entry of new participants through individual fishing quotas (IFQs)
[@grimm2012].

@@

Using a unique dataset collected over 30 years on individual fishers, rather
than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals we can track
people that switch fishery permits over time or use multiple vessels. Similarly,
we can disentangle fishers that share the same vessel. We develop and apply
a hierarchical Bayesian model to understand the effect of fisheries catch
species diversity on individual revenue and revenue variability that builds on
results from vessel [@kasperski2013], fleet [@sethi2012b], and community-level
[@sethi2014] variability. We develop a variance-function regression model
[@davidian1987; @hall1989], to simultaneously model changes in the mean and
variance of individual revenue as a function of covariates. We simultaneously
estimate the effect of species diversity (the inverse of Simpson's diversity
index [@simpson1949; @jost2006]) on individual revenue and revenue variability,
and estimate effects both within and across fishing strategies while controlling
for fishing effort and latent time effects (e.g. changing environmental
conditions). To our knowledge, this is the first application of this type of
model in any natural resource field.

@@

We evaluated trends in revenue and diversification over time for individuals
fishing commercially in Alaska from 1985--2014 (Fig. \ref{fig:ts}A). The
majority (70--90%) hold a single permit, with a slight increase in single-permit
holders since 2000 (Fig. \ref{fig:ts}C). This overall trend is most sensitive to
halibut or salmon permit holders --- compared to other fisheries, halibut permit
holders are more likely to hold halibut plus other permits, whereas salmon
permit holders are more likely to hold a single permit (Fig. \ref{fig:ts}C).
Despite making up only 10--30% of the individuals, multiple-permit holders earn
approximately half the overall revenue (Fig. \ref{fig:ts}B). The mean species
diversity of this revenue declined somewhat from 1980--2000 but has since
remained steady (Fig. \ref{fig:ts}D). However, this trend appears largely driven
by an increase in salmon specialists in the 1980s and 1990s --- the trend
disappears if salmon license holders are excluded (Fig. \ref{fig:ts}D).

@@

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994, which potentially confounds our estimates with
a major regulatory change. Therefore, we refit our models allowing all
strategy-level effects involving halibut and sablefish permits to vary
separately before and after the introduction of IFQs. The introduction of IFQs
reduced variability by ~25% (TODO XX--XX 95% CI) for individuals with only
halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).

@@

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies that exploit a diversity of assets provides substantial
benefits over strategies with lower diversity [@baldursson1997; @hilborn2001;
@edwards2004]. However, in practice, the ability of individuals to effectively
diversify is limited by regulation and market forces. Here we document the
effect of individual-level changes in species diversity on revenue and revenue
variability across three scales. We find that (1) individuals with sets of
permits that allow high levels of species diversity tend to have lower revenue
variability. (2) Adding a fisheries permit usually increases revenue and
decreases revenue variability. However, (3) within the constraints of a permit
and accounting for effort, specializing tends to increase revenue while both
specializing and generalizing tend to correlate with greater revenue variability
with considerable differences amongst fisheries. Thus, the most effective
mechanism by which species diversity can lower revenue variability for
individual fishers --- switching or adding fishing permits --- is expensive,
limited by regulations, and consequently unavailable to many individuals.

@@

There are many possible barriers to diversification for individuals relying on
natural resources for their livelihood. A primary barrier is the cost of
diversifying. For commercial fishers, purchasing additional licenses and gear
typically represents a substantial expense. Related barriers are apparent in
other natural resource sectors. For example, diversification has been positively
linked with total income or access to financial capital for farmers
[@abdulai2001; @barrett2001], small-scale fishing communities [@olale2012], and
those relying on forest resources [@illukpitiya2008]. Another major barrier to
diversification can be management restrictions. In commercial fisheries,
regulations that you have been shown to reduce overfishing --- including
improved assessments [@melnychuk2017] and individual quota systems
[@costello2008] --- may ultimately restrict individual diversification
[@smith1986; @kasperski2013] or at least make developing a diverse fishing
portfolio more expensive. However, individual quota systems, in particular, may
also reduce income variability (Fig. S\ref{fig:ifq}A) perhaps offsetting the
effects of reduced diversification [@holland2016].

@@

\caption{Trends in revenue and diversification over time. (A) Map of fishing
regions in Alaska, USA. (B) Total revenue in billions of 2009 USD from `r
range_yrs[1]` to `r range_yrs[2]` for multiple (grey) and single (blue) permit
holders. (C) Proportion of single permit holders for all fisheries (thick black
line) and with permit holders omitted each year who fished any of the `r
n_jacknifed` top species groups (thin lines). (D) Mean effective diversity of
species fished (Simpson's diversity index) for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the `r n_jacknifed`
top species groups (thin lines). } \label{fig:ts} \end{center} \end{figure}

@@

We obtained commercial fisheries landings and revenue data for all permit
holders in Alaska from `r range_yrs[1]` to `r range_yrs[2]` from the Alaskan
Commercial Fisheries Entry Commission (CFEC). These data represent a total of
nearly `r round(ndat$initial_tot_rev/1e9)` billion 2009 USD. We adjusted for
inflation by setting all revenues to 2009 USD [@bea2016]. We implemented
a number of filtering steps to focus on individuals actively engaged in
commercial fishing (Supporting Information). In particular, we removed permit
holders whose median revenue was less than \$10,000 2009 USD to focus on
individuals for whom commercial fishing formed a substantial part of their
income.

We used combinations of state and federal fishing permits held by an individual
in a specific year to define fishing "strategies", representing the species
targeted (Supporting Information). For example, we combined permits that were
otherwise the same except for vessel size (e.g. a longliner fishing sablefish
on a vessel under 60 ft was considered to have the same strategy as a longliner
fishing sablefish on a vessel over 60 ft), and we combined a number of permits
that were targeting a single species and differed only in region fished.
Therefore, for example, someone fishing herring roe in Kodiak and someone
fishing herring roe in Alaska Peninsula were both considered to have a "herring
roe" permit group. For salmon permits, we formed salmon strategies based on
similarities in gear type and species composition (Supporting Information).

@@

We use $\log(R_{i,t-1}$) as an offset, and thus our model describes the log
ratio of revenue from year-to-year, i.e., $\log(R_{i,t}) - \log(R_{i,t-1})
= \log(R_{i,t}/R_{i,t-1})$. We model change in revenue because preliminary
analysis revealed non-stationary trends in revenue (resulting from experience or
other unmodeled factors). This approach eliminates having to deal with the
non-stationary time series and eliminates having to estimate thousands of
mean-revenue intercepts associated with individual fishers. We removed
person-year combinations without a subsequent year of revenue.

@@

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.
The estimated $\beta_{j,t}$'s represent years when people with a particular set
of permits tended to collectively do better or worse than the long-term average
(Fig. S\ref{fig:str-yrs}). Therefore, an individual's expected change in revenue
(and variability) is after accounting for the general trend in revenue for that
set of permits.

>>>>

Individuals relying on the extraction of natural resources for their livelihood
--- fishers, farmers, miners, and loggers, among others --- face high levels of
income variability driven by a mix of environmental, biological, management, and
economic dynamics. A key component to managing these industries is identifying
how regulatory actions and individual behaviour affect income variability and by
extension economic stability and the sustainable use of natural resources. For
commercial fisheries, communities and vessels fishing a greater diversity of
species have less revenue variability than those fishing a lower diversity.
However, it is unclear if these benefits extend to the actions of individual
fishers and how year-to-year changes in diversification affect revenue and
revenue variability. Here, we identify three axes by which fishers in Alaska,
one of the world's most productive fishing regions, can diversify fishing
activities. We show that, despite increasing specialization over the last 30
years, fishing permits with higher species diversity reduces individual revenue
variability and fishing an additional permit is associated with higher revenue
and lower variability. However, increasing species diversity within the
constraints of existing permits has a fishery-dependent effect on revenue and is
usually (`r g2_dens`% probability) associated with increased revenue uncertainty
the following year. Our results demonstrate that the most effective option for
individuals to decrease revenue variability is to purchase permits to
participate in additional or more diverse fisheries. However, this option is
expensive, often limited by regulations such as catch share programs, and
consequently unavailable to many individuals. With increasing environmental
variability in a changing climate, it will be particularly important that
individuals relying on natural resources for their livelihood have effective
strategies to reduce income variability.

@@

<!-- rotate -> plant multiple? -->

Individuals who rely on natural resources for income develop strategies to
reduce income variability. For example, farmers may rotate their crops to buffer
short-term climate variation and long-term environmental trends [@zentner1988].
Similarly, loggers maintain a diverse mix of tree species, age structure, and
harvest in multiple areas to buffer against disease outbreak, wildfires, and
price variation (REF). However, otherwise well-intentioned regulations may limit
how individuals diversify, or incentivize against diversification. For example,
in terrestrial agriculture, crop subsidies in the U.S. may incentivize some
farms to specialize (e.g. dairy, grains, soybeans; @mishra2002). In other
instances, external market forces (e.g. prices or demand) may discourage the
adoption of diverse strategies and help promote specialization [@bradshaw2004].

@@

<!-- important to acknowledge that IFQ regs have been implemented partly for economic -->
<!-- reasons and have been successful by some economic measures. Might even want to -->
<!-- insert the above sentence. -->

The state and federal fisheries of Alaska provide a unique opportunity to
understand the role of individuals' strategies in determining income and income
variability. Fisheries in Alaska are among the highest-valued fisheries in the
world with ~2.7 billion kg landed biomass valued at nearly 2 billion USD
annually [@nmfs2016]. The days of open, unregulated fisheries in most developed
countries have passed --- fishers must own a license to participate in virtually
all fisheries [@hilborn2003a]. While such regulations have helped reduce
overfishing and in many fisheries have increased profits, they limit the
available strategies to reduce income variability. For example, many permits
limit fishing to a single species, diversifying by purchasing additional fishing
permits can be expensive[^1], and some fisheries limit the entry of new
participants through individual fishing quotas (IFQs) [@grimm2012].

@@

Using a unique dataset collected over 30 years on individual fishers, rather
than fleets or vessels, we examine how revenue and revenue variability of
individuals is affected by diversification. By tracking individuals we can track
people that switch fishery permits over time or use multiple vessels. Similarly,
we can disentangle fishers that share the same vessel. We develop and apply
a hierarchical Bayesian model to understand the effect of species diversity
within fisheries catches on individual revenue and revenue variability. Our
model builds on results from vessel [@kasperski2013], fleet [@sethi2012b], and
community-level [@sethi2014] variability. We develop a variance-function
regression model [@davidian1987; @hall1989], to simultaneously model changes in
the mean and variance of individual revenue as a function of covariates. We
simultaneously estimate the effect of species diversity (the inverse of
Simpson's diversity index [@simpson1949; @jost2006]) on individual revenue and
revenue variability, and estimate effects both within and across fishing
strategies while controlling for fishing effort and latent time effects (e.g.
changing environmental conditions). To our knowledge, this is the first
application of this type of model in any natural resource field.

@@

We evaluated trends in revenue and diversification over time for individuals
fishing commercially in Alaska from 1985--2014 (Fig. \ref{fig:ts}A). The
majority (70--90%) hold a single permit, with a slight increase in single-permit
holders since 2000 (Fig. \ref{fig:ts}C). This overall trend is most sensitive to
halibut or salmon permit holders --- compared to other fisheries, halibut permit
holders are more likely to hold halibut plus other permits, whereas salmon
permit holders are more likely to hold a single permit (Fig. \ref{fig:ts}C).
Despite making up only 10--30% of the individuals, multiple-permit holders earn
approximately half the overall revenue (Fig. \ref{fig:ts}B). The mean species
diversity of this revenue declined somewhat from 1985--2000 but has since
remained steady (Fig. \ref{fig:ts}D). However, this trend appears largely driven
by an increase in salmon specialists in the 1980s and 1990s --- the trend
disappears if salmon license holders are excluded (Fig. \ref{fig:ts}D).

@@

Alaskan halibut and sablefish fisheries were converted to individual fishery
quota (IFQ) management in 1994, which potentially confounds our estimates with
a major regulatory change. Therefore, we refit our models allowing all
strategy-level effects involving halibut and sablefish permits to vary
separately before and after the introduction of IFQs. The introduction of IFQs
reduced variability in revenue by ~25% (TODO XX--XX 95% CI) for individuals with
only halibut or sablefish permits (Fig. S\ref{fig:ifq}A). Furthermore, for most
strategies, the association between changing species diversity and increased
revenue variability became stronger after the introduction of IFQs (Fig.
S\ref{fig:ifq}B). This was especially true for individuals fishing only halibut
or sablefish and less so for individuals combining halibut or sablefish with
a salmon permit (Fig. S\ref{fig:ifq}B).

@@

For individuals deriving livelihoods from natural resources, theory suggests
that adopting strategies that exploit a diversity of assets provides substantial
benefits over strategies with lower diversity [@baldursson1997; @hilborn2001;
@edwards2004]. However, in practice, the ability of individuals to effectively
diversify is limited by regulation and market forces. Here we document the
effect of individual-level changes in fished species diversity on revenue and
revenue variability across three scales. We find that (1) individuals with sets
of permits that allow high levels of species diversity tend to have lower
revenue variability. (2) Adding a fisheries permit usually increases revenue and
decreases revenue variability. However, (3) within the constraints of a permit
and accounting for effort, specializing tends to increase revenue while both
specializing and generalizing tend to correlate with greater revenue variability
with considerable differences amongst fisheries. Thus, the most effective
mechanism by which species diversity can lower revenue variability for
individual fishers --- switching or adding fishing permits --- is expensive,
limited by regulations, and consequently unavailable to many individuals.

@@

There are many possible barriers to diversification for individuals relying on
natural resources for their livelihood. A primary barrier is the cost of
diversifying. For commercial fishers, purchasing additional licenses and gear
typically represents a substantial expense. Related barriers are apparent in
other natural resource sectors. For example, diversification has been positively
linked with total income or access to financial capital for farmers
[@abdulai2001; @barrett2001], small-scale fishing communities [@olale2012], and
those relying on forest resources [@illukpitiya2008]. Another major barrier to
diversification can be management restrictions. In commercial fisheries,
regulations that have been shown to reduce overfishing --- including improved
assessments [@melnychuk2017] and individual quota systems [@costello2008] ---
may ultimately restrict individual diversification [@smith1986; @kasperski2013]
or at least make developing a diverse fishing portfolio more expensive. However,
individual quota systems, in particular, may also reduce income variability
(Fig. S\ref{fig:ifq}A) perhaps offsetting the effects of reduced diversification
[@holland2016].

@@

\caption{Trends in revenue and diversification over time. (A) Map of fishing
regions in Alaska, USA. (B) Total revenue in billions of USD from `r
range_yrs[1]` to `r range_yrs[2]` for multiple (grey) and single (blue) permit
holders. (C) Proportion of single permit holders for all fisheries (thick black
line) and with permit holders omitted each year who fished any of the `r
n_jacknifed` top species groups (thin lines). (D) Mean effective diversity of
species fished (Simpson's diversity index) for all fisheries (thick black line)
and with permit holders omitted each year who fished any of the `r n_jacknifed`
top species groups (thin lines). } \label{fig:ts} \end{center} \end{figure}

@@

We obtained commercial fisheries landings and revenue data for all permit
holders in Alaska from `r range_yrs[1] - 1` to `r range_yrs[2]` from the Alaskan
Commercial Fisheries Entry Commission (CFEC). These data represent a total of
nearly `r round(ndat$initial_tot_rev/1e9)` billion 2009 USD. We adjusted for
inflation by setting all revenues to 2009 USD [@bea2016]. We implemented
a number of filtering steps to focus on individuals actively engaged in
commercial fishing (Supporting Information). In particular, we removed permit
holders whose median revenue was less than \$10,000 USD to focus on individuals
for whom commercial fishing formed a substantial part of their income.

<!-- TODO Jordan: held by active fishers were not included in permit counts -->
<!-- / portfolios? Disregard this comment as you please but I thought I’d mention. -->

We used combinations of state and federal fishing permits held by an individual
in a specific year to define fishing "strategies", representing the species
targeted (Supporting Information). For example, we combined permits that were
otherwise the same except for vessel size (e.g. a longliner fishing sablefish
on a vessel under 60 ft was considered to have the same strategy as a longliner
fishing sablefish on a vessel over 60 ft), and we combined a number of permits
that were targeting a single species and differed only in region fished. For
example, someone fishing herring roe in Kodiak and someone fishing herring roe
in Alaska Peninsula were both considered to have a "herring roe" permit group.
For salmon permits, we formed salmon strategies based on similarities in gear
type and species composition (Supporting Information).

@@

We use $\log(R_{i,t-1}$) as an offset, and thus our model describes the log
ratio of revenue from year-to-year, i.e., $\log(R_{i,t}) - \log(R_{i,t-1})
= \log(R_{i,t}/R_{i,t-1})$. We model change in revenue because preliminary
analysis revealed non-stationary trends in revenue (resulting from experience or
other unmodelled factors). This approach eliminates having to deal with the
non-stationary time series and eliminates having to estimate thousands of
mean-revenue intercepts associated with individual fishers. We removed
person-year combinations without a subsequent year of revenue.

@@

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.
The estimated $\beta_{j,t}$'s represent years when people with a particular set
of permits tended to collectively do better or worse than the long-term average
(Fig. S\ref{fig:str-yrs}). Therefore, an individual's expected change in revenue
(and variability) represents the expectation after accounting for the general
trend in revenue for that set of permits.

### 2017-01-06 portfolio/text/supp.Rnw
Add effort fig
Trivial tweaks
Jordan and Milo edits

We then proceeded to combine similar permits in the following steps.
We combined a number of permits that were the same except for vessel size.
We combined permits for
otter troll,
longline finfish,
pot gear.
king crab,
and
shrimp.
We grouped a number of permits that were targeting a single species
and differed only in region fished.
For example, someone fishing herring roe in Kodiak (G34K)
and someone fishing herring roe in Alaska Peninsula (G34M)
were both considered to have a herring roe permit strategy.
We combined permits across each of
dungeness crab,
herring roe purse seining,
herring roe gillnet,
herring hand picked,
herring pound fishing,
sea cucumber,
sea urchin,
tanner crabs

@@

@@

TODO length(unique(pholders))
% Rows of data: \Sexpr{ndat$final}
% Number of permit holders: \Sexpr{npholders}
% Range of years: \Sexpr{range_yrs}
% Number of strategy-years: \Sexpr{nstr_yrs}
% \Sexpr{nstrat$enough_pholders}
% \Sexpr{round(ndat$rev_enough_pholders/1e9,2)}
% lost \% rev no strat:
% \Sexpr{round(ndat$rev_after_no_na_strat/ndat$rev_b4_no_na_strat,2)*100}
% lost rows no strat:
% \Sexpr{round(ndat$after_no_na_strat/ndat$b4_no_na_strat,2)*100}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{The effect of adding a permit to ones strategy
on estimated revenue variability and median revenue.
This is an extended version of Fig.~2 that includes all major
strategy combinations.}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid.png}
\caption{The log-absolute value residuals from the mean-component model (Eq.~\ref{eq:mean}).
It is these residuals that are modeled in the variance-component model
(Eq.~\ref{eq:cv}).
Breakpoint linear regression fits are overlaid in red for visual interpretation.}
\label{fig:resid}
\end{center}
\end{figure}

@@

>>>>

We then proceeded to combine similar permits in the following steps.
We combined a number of permits that were the same except for vessel size.
We combined permits for
otter trawl,
longline finfish,
pot gear.
king crab,
and
shrimp.
We grouped a number of permits that were targeting a single species
and differed only in region fished.
For example, someone fishing herring roe in Kodiak (G34K)
and someone fishing herring roe in Alaska Peninsula (G34M)
were both considered to have a herring roe permit strategy.
We combined permits across each of
dungeness crab,
herring roe purse seining,
herring roe gillnet,
herring hand picked,
herring pound fishing,
sea cucumber,
sea urchin, and
tanner crabs.

@@

% TODO: Are you saying that PWS sockeye permits were combined with BB sockeye permits?I can't remember but that's what it sounds like so I just wanted to be clear.

@@

% TODO length(unique(pholders))
% Rows of data: \Sexpr{ndat$final}
% Number of permit holders: \Sexpr{npholders}
% Range of years: \Sexpr{range_yrs}
% Number of strategy-years: \Sexpr{nstr_yrs}
% \Sexpr{nstrat$enough_pholders}
% \Sexpr{round(ndat$rev_enough_pholders/1e9,2)}
% lost \% rev no strat:
% \Sexpr{round(ndat$rev_after_no_na_strat/ndat$rev_b4_no_na_strat,2)*100}
% lost rows no strat:
% \Sexpr{round(ndat$after_no_na_strat/ndat$b4_no_na_strat,2)*100}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{The effect of adding a permit to one's strategy
on estimated revenue variability and median revenue.
This is an extended version of Fig.~2 that includes all major
strategy combinations.}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid.png}
\caption{The log-absolute value residuals from the mean-component model (Eq.~\ref{eq:mean}).
These residuals are modelled in the variance-component model
(Eq.~\ref{eq:cv}).
Breakpoint linear regression fits are overlaid in red for visual interpretation.}
\label{fig:resid}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../figs/stan-offset-break-anti-spaghetti-specializing-no-effort.pdf}
\caption{Same as Fig.~4 but without the effort (days fished) predictor and
  without its interaction with species diversity.}
\label{fig:noeffort}
\end{center}
\end{figure}
